### 2015-02-03 report/preamble.tex
Force use of English number formatting
Rewrite results, add graphs

\usepackage{url}
\usepackage{numprint}

@@

width=.35\textwidth,
height=.3\textwidth,

@@

\pgfplotsset{datasetsCDF/.style=
{
xmin=0,
xmax=1,
ymin=0,
ymax=1,
grid=both,
xtick={0,.1,...,1.1},
ytick={0,.1,...,1.1},
enlargelimits=false,
% Marks 0% and 99%.
mark repeat=99,
% Using a custom position below.
% legend pos=south east,
legend style={
at={(.99,.01)},
anchor=south east,
cells={anchor=west},
},
},
datasetsCDFFullPage/.style=
{
width=\textwidth,
height=1.46\textwidth,
}
}

\pgfplotsset{datasetsOccurances/.style=
{
ymin=,
xmin=0.1,
xmax=100,
xtick={0.1,1,2,3,4,5,10,20,50,100},
minor xtick={6,7,8,9,30,40,60,70,80,90},
xticklabel={%
	\ifnum\ticknum=9%
		$100^+$%
	\else%
		\pgfmathfloatparsenumber{\tick}%
		\pgfmathfloatexp{\pgfmathresult}%
		\pgfmathprintnumber[fixed,precision=0]{\pgfmathresult}%
	\fi%
},
yticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill,
/pgf/number format/precision=2
},
% Marks 0.1.
mark repeat=1,
mark indices={1},
}
}

>>>>

\usepackage{url}
\usepackage{numprint}
\npstyleenglish

@@

width=.4\textwidth,
height=.325\textwidth,

@@

\pgfplotsset{datasetsCDF/.style=
{
xmin=0,
xmax=1,
ymin=0,
ymax=1,
grid=both,
xtick={0,.1,...,1.1},
ytick={0,.1,...,1.1},
enlargelimits=false,
% Marks 0% and 99%.
mark repeat=99,
% Using a custom position below.
% legend pos=south east,
legend style={
at={(.99,.01)},
anchor=south east,
cells={anchor=west},
},
},
datasetsCDFFullPage/.style=
{
width=\textwidth,
height=1.46\textwidth,
},
datasetsCDFMiniResults/.style=
{
width=.4\textwidth,
height=.325\textwidth,
font=\tiny,
xtick={0,.2,...,1.0},
ytick={0,.2,...,1.0},
minor xtick={0,.1,...,1.1},
minor ytick={0,.1,...,1.1},
xticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill=false,
/pgf/number format/precision=1
},
yticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill=false,
/pgf/number format/precision=1
},
title style={at={(.5,.95)}},
}
}

\pgfplotsset{datasetsOccurances/.style=
{
ymin=,
xmin=0.1,
xmax=100,
xtick={0.1,1,2,3,4,5,10,20,50,100},
minor xtick={6,7,8,9,30,40,60,70,80,90},
xticklabel={%
	\ifnum\ticknum=9%
		$100^+$%
	\else%
		\pgfmathfloatparsenumber{\tick}%
		\pgfmathfloatexp{\pgfmathresult}%
		\pgfmathprintnumber[fixed,precision=0]{\pgfmathresult}%
	\fi%
},
yticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill,
/pgf/number format/precision=2
},
% Marks 0.1.
mark repeat=1,
mark indices={1},
},
datasetsOccurancesMiniResults/.style=
{
width=.35\textwidth,
height=.325\textwidth,
font=\tiny,
xmax=15,
xtick={0.1,1,5,10,15},
ytick={0,.2,...,1.0},
minor xtick={2,3,4,6,7,8,9,11,12,13,14},
xticklabel={%
	\pgfmathfloatparsenumber{\tick}%
	% \pgfmathfloatexp{\pgfmathresult}%
	\pgfmathprintnumber[fixed,precision=0]{\pgfmathresult}%
},
minor ytick={0,.1,...,1.1},
yticklabel style={
/pgf/number format/fixed,
/pgf/number format/fixed zerofill=false,
/pgf/number format/precision=1
},
title style={at={(.5,.95)}},
},
}

### 2015-02-03 report/tableread.tex
Add CDF from datasets.non-failed.ratio-buckets.is-disconnect-match.normalized.cumulative.sorted.tsv
Rewrite results, add graphs

@@

>>>>

\pgfplotstabletranspose[
	colnames from=Dataset
	]\tableTransposedDatasetsNonFailedRatioBucketsIsDisconnectMatchNormalizedCumulativeSorted{datasets.non-failed.ratio-buckets.is-disconnect-match.normalized.cumulative.sorted.tsv}

@@

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.classification.secure.coverage.sorted.summary.tsv}\tableDatasetsNonFailedClassificationSecureCoverageSortedSummary

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.disconnect.organizations.coverage.external.sorted.summary.tsv}\tableDatasetsNonFailedDisconnectOrganizationsCoverageExternalSortedSummary

\pgfplotstableread[
		format=file,
		col sep=tab,
	]{datasets.non-failed.disconnect.categories.coverage.external.sorted.summary.tsv}\tableDatasetsNonFailedDisconnectCategoriesCoverageExternalSortedSummary
